\documentclass[11pt,fancychapters, table, xcdraw]{report}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{listings}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{acro}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{subcaption}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{wrapfig}

\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}

\graphicspath{ {./images/} }
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=python,
  aboveskip=5mm,
  belowskip=5mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\usetikzlibrary{calc,trees,positioning,arrows,chains,shapes.geometric,%
    decorations.pathreplacing,decorations.pathmorphing,shapes,%
    matrix,shapes.symbols}
\include{acronyms}
\geometry{top=1.3in,bottom=1.3in}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\definecolor{DarkerGreen}{RGB}{0,179,45}

\include{python_highlighting}

\newtheorem{exmp}{Example}[section]

\newcommand{\codeExample}[2]{
	\begin{exmp}
      #1
      \noindent\begin{minipage}{\linewidth}
      \begin{lstlisting}[style=python]
          #2
      \end{lstlisting}
      \end{minipage}
    \end{exmp}
}

\newcommand\MyLBrace[2]{%
  \left.\rule{0pt}{#1}\right\}\text{#2}}
  
\tikzset{
>=stealth',
  punktchain/.style={
    rectangle, 
    rounded corners, 
    % fill=black!10,
    draw=black, very thick,
    text width=10em, 
    minimum height=3em, 
    text centered, 
    on chain},
  line/.style={draw, thick, <-},
  element/.style={
    tape,
    top color=white,
    bottom color=blue!50!black!60!,
    minimum width=8em,
    draw=blue!40!black!90, very thick,
    text width=10em, 
    minimum height=3.5em, 
    text centered, 
    on chain},
  every join/.style={->, thick,shorten >=1pt},
  decoration={brace},
  tuborg/.style={decorate},
  tubnode/.style={midway, right=2pt},
}

\title{Vehicle-To-Vehicle Communication (V2V)}
\author{Supervised by: Dr. Mohammed S. A. Mossaad}

\date{
\begin{table}[h]
\def\arraystretch{1.5}
\centering
\begin{tabular}{| c | c |}
\hline
 \textbf{ID} &  \textbf{Name} \\
 \hline
 7 &  Aya Abd Elaziz Mohamed  \\
 \hline
  12 & Ahmed Gamal Ahmed\\
 \hline
 24 & Ahmed Adel Sultan\\
 \hline
 40 & Ahmed Haitham Ahmed \\
 \hline
  146 & Kerollos Emad Sobhy \\
 \hline
  210 & Moaaz Mahmoud Elsayed \\
 \hline
  262 & Yousra Mamdouh Ali \\
 \hline
  264 & Youmna Ahmed Mahmoud\\
 \hline
\end{tabular}
\end{table}
}
\begin{document}

\maketitle

\pagenumbering{gobble}
\newpage
\pagenumbering{roman}
\newpage
Thanks to our supervisor Dr. Mohamed Salah who has been nothing but a helpful mentor in every step along the way. And special thanks to all our friends and families without whom our work would have never seen the light.
\newpage
\begin{abstract}
    Vehicles became a necessity in our life more than a luxury in the past decade. There is almost no one who does not use vehicles these days whether it is public transportation or personal car. So, the evolution of technology -related to vehicle- was a must. \newline \newline
    Despite of necessity of the vehicles, accidents increase day by day and this problem has to be solved, so Intelligent Transportation Systems appeared, they are systems that aim to enhance driver assistance, which decreases the number of accidents substantially. Vehicle-to-vehicle (V2V) is a part of these systems, it allows the vehicles to communicate, giving warnings that help us avoid life-threatening accidents. \newline \newline
    V2V  server consists of two main units; clients and server, each client can act as both transmitter and receiver, the target of V2V is to make a communication system between these clients by the server. Clients are units that are placed in each vehicle and be a part of it “so the clients are the vehicles”, and the server is a network to create a communication way between these vehicles. \newline \newline
    V2V communication is developed continuously and this project target is to implement a best design for V2V with less cost and more efficiency.\\
    The project is related to Internet of things, Embedded systems, and  Machine Learning Technologies.
\end{abstract}
\tableofcontents
\newpage
\pagenumbering{arabic}

\include{chp1}
\include{chp2}
\include{chp3}
\include{chp4}
\include{chp5}
\include{chp6}
\include{chp7}
\include{chp8}
\include{chp9}
\include{chp10}
\include{references}

\end{document}